%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Principal Engineer - Development} % Job title
    {Indix} % Organization
    {Chennai, India} % Location
    {Oct. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tech Lead in Seeder, Crawler and Parser (SCP) team}
        \item {Finder - HTML Archive Storage system for storing over 3 billion HTML documents}
        \item {\href{https://github.com/ashwanthkumar/suuchi}{Suuchi} - OpenSource toolkit to build distributed data systems. Built for Finder initially but later adopted to other projects as well.}
        \item {\href{https://github.com/ashwanthkumar/gotlb}{GoTLB} - TCP Load balancer with automated service discovery for apps running on Marathon.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Principal Engineer - DevOps} % Job title
    {Indix} % Organization
    {Chennai, India} % Location
    {Oct. 2015 - Sept. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Responding to Infrastructure queries / requests}
        \item {Reviewing Pull Requests for Provisioning, monitoring and deployment}
        \item {Work with tools like - Ansible, Chef, Mesos, Marathon, Go.CD, Hadoop and AWS}
        \item {Built some tools around automation like - \href{https://github.com/ashwanthkumar/marathon-alerts}{marathon-alerts}, \href{https://github.com/ashwanthkumar/gocd-janitor}{gocd-janitor}, \href{https://github.com/indix/vamana}{vamana}, \href{https://github.com/indix/matsya}{matsya}, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Indix} % Organization
    {Chennai, India} % Location
    {Jun. 2012 - Sept. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {First generation of Indix Data Pipeline which is completely based out of λ architecture. }
        \item {Two generations of our web crawler - scaling to millions of pages per day across 1000s of websites. }
        \item {Two generations of Scheduler which feeds our crawler with the right urls every day - this is by far the most challenging work especially since the data we collect decays (little slowly) over time (product pricing information) and
        we should always be on the top when freshness drops. }
        \item {Three generations for Product Parser. In the third generation I was responsible in coming up with a DSL to express extractions so that we can outsource the tagging outside.}
        \item {From Java based MR jobs to Scalding to building a query tool with a DSL (inspired from SQL and on top of scalding) which enabled engineers for faster access to data for analysis / debugging.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Big Data Intern} % Job title
    {Mu Sigma} % Organization
    {Bangalore, India} % Location
    {Jan. 2012 - May. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Evaluating AWS for migrating to cloud from custom data centers}
        \item {Worked on running R code on Storm.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
