%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{ Go CD Tools/Plugins }

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Scale GoCD Agents on demand with Docker} % Description
    {\href{https://github.com/ashwanthkumar/vasuki}{vasuki}} % Project title
    {Feb. 2016} % Date(s)
    {} % Ignore
    {
    Vasuki is a \href{https://www.go.cd/}{GoCD} agent autoscaler. Currently it uses docker to bring up agents on demand and scale them back down.
    You just have to launch a Vasuki instance for an environment and resources with a docker image.
    You can run as many Vasuki instances in a machine for various environments / resources.
    }

%---------------------------------------------------------
  \cventry
    {More intelligent GoCD purge policy} % Description
    {\href{https://github.com/ashwanthkumar/gocd-janitor}{gocd-janitor}} % Project title
    {Dec. 2015} % Date(s)
    {} % Ignore
    {
    Tiny java program that helps you with cleaning up artifacts on \href{https://go.cd/}{GoCD} servers.
    There was a \href{https://groups.google.com/forum/#!topic/go-cd/HfOY_74OKhI/discussion}{discussion} on GoCD mailing list and
    my own not-so-good experience managing artifacts on GoCD led me to this.
    }

%---------------------------------------------------------
  \cventry
    {GoCD Plugin to send pipeline notifications to an instance of Badge Server} % Description
    {\href{https://github.com/ashwanthkumar/gocd-build-badge-notifier}{gocd-build-badge-notifier}} % Project title
    {Nov. 2015} % Date(s)
    {} % Ignore
    {
    gocd-build-badge-notifier is a notification plugin that pushes pipeline build status to an instance of Build Badge Server.
    It goes well with a hosted version of \href{https://github.com/ashwanthkumar/gocd-build-badge-server}{Build Badge Server}.
    }

%---------------------------------------------------------
  \cventry
    {Build Badge for your GoCD builds} % Description
    {\href{https://github.com/ashwanthkumar/gocd-build-badge-server}{gocd-build-badge-server}} % Project title
    {Nov. 2015} % Date(s)
    {} % Ignore
    {
    gocd-build-badge-server is NodeJS based server to serve your build badges for embedding them on Github / Bitbucket.
    }

%---------------------------------------------------------
  \cventry
    {GoCD plugin to build PRs for a Github repo} % Description
    {\href{https://github.com/ashwanthkumar/gocd-build-github-pull-requests}{gocd-build-github-pull-requests}} % Project title
    {March 2015} % Date(s)
    {} % Ignore
    {
    GoCD SCM plugin for Git feature branch support.
    }

%---------------------------------------------------------
  \cventry
    {GoCD plugin to push build notifications to Slack} % Description
    {\href{https://github.com/ashwanthkumar/gocd-slack-build-notifier}{gocd-slack-build-notifier}} % Project title
    {March 2015} % Date(s)
    {} % Ignore
    {
    GoCD plugin to push build notifications to Slack or any Slack API compatible systems like Rocket.Chat.
    }

%---------------------------------------------------------
\end{cventries}
